Cover letter for the IJRR submission \\ ``An efficient acyclic contact planner for multiped robots''

### 2017-01-23 cover2.tex
[COVER] Minor final remark.

\subsection{Reviewer 1}
\noindent
\begin{longtable}{|p{21em}|p{21em}|}
\hline
The paper addresses an important problem of planning robot motion involving contacts. It extends the idea of planning acyclic contacts by decoupling the issue into (1) planning a guide path for the root of the robot, and (2) planning a discrete sequence of acyclic and static equilibrium contact configurations along the path, with an interpolation of motion between two consecutive contact postures in the sequence. The introduced planner considers both collision avoidance and maintenance of desired contacts and aims at real-time or interactive performance. 
&Thanks for the comment.
\\ \hline % ----------------------------------------------------------------------------------
For the decoupled approach to work, the planned guide path must guarantee that a sequence of stable contact configurations is associated with it to execute the path with desired contacts and yet without undesired collisions; such a guide path is called “equilibrium feasible”. The issue is how to find such a guide path efficiently. One key assumption of the paper is that for cluttered environments, “most of the times” a guide path that is “contact feasible” (referring to that at least one end-effector is in contact with the environment and there is no undesired collision between the robot and the environment) is also “equilibrium feasible”. It further assumes that if the reachable space of the robot along the guide path is in collision with the environment but the robot root configuration is not in collision, called the “reachability condition”, then the guide path is “contact feasible”. With those assumptions, the paper treated guide path planning as a geometric problem and used an RRT planner to solve the problem. 
& We agree with this summary.
\\ \hline % ----------------------------------------------------------------------------------
However, the question is whether the above key assumption (of 
“contact feasible” implies “equilibrium feasible”) is reasonable. The paper did not provide justification for the assumption, and the assumption does not seem intuitive. The paper used terms such as “most of the times” and “cluttered contact planning” without clear and quantifiable definitions. With the above assumptions, planning becomes quite straightforward, and the planning algorithm used is rather conventional. 
&
We modified the paper to more rigorously discuss these hypotheses. 
We also believe that the main justification of their validity is shown by the statistical tests we provide in the result section.\newline
See Section 6 for details. 
\\ \hline % ----------------------------------------------------------------------------------
For the next problem of planning a sequence of contact configurations given a “contact feasible” root path, the paper further decomposed the problem by planning the configuration of one limb at a time, assuming the root configuration and the other limb configurations were fixed. For each limb, N sampled configurations were considered (sampled off-line), and they were indexed by the corresponding end-effector position and stored in an octree beforehand. 
Because all that was done off-line, it is not clear how N was decided. 
&
As explained in the paper, in our previous work (Tonneau et al. 2014), we discussed in details  how to choose N. We chose to refer to the paper rather than giving details  because of the space constraints of
the paper. In our experiments,
we always set $N=10000$.

@@

\\ \hline % ----------------------------------------------------------------------------------
The main issue with the proposed planner is that assumptions (commented earlier) and decisions were made in the planner conveniently in order to simplify the problem but without much justification, and there is no guarantee of a solution. The entire approach is heuristic and somewhat ad hoc. 
&
As detailed in Section~\ref{orig} of this cover letter, we disagree regarding the fact that our approach is purely heuristic.
We claim that the dimensionality reduction proposed to address \mP1 is an important contribution to the field.

@@

\newpage
\subsection{Reviewer 2}
\noindent
\begin{longtable}{|p{21em}|p{21em}|}
\hline
The paper presents a method for producing contact plans for the locomotion of multiped robots. It decomposes the problem into two sub-problems : the computation of a guide path is which the robot is floating close enough to the environment, and subsequently the positioning of contacts on the environment along the guide.
& Thanks for this summary, that we agree with.
\\ \hline % ----------------------------------------------------------------------------------
My major concern about this piece of work is its lack of originality. The problem seems to have been well formalized and studied in numerous previous works (Hauser et al, Escande et al, etc.). The authors experiment with minor heuristic adjustments. I do not consider them as major contributions that warrant a publication in IJRR by the standards of the journal. The authors end up with the main claim of the paper being a reduced computation time in comparison with these previous works. As admitted by the authors themselves, even this gain in computation time is not really comparable to the previous works since the outputs are different (previous works go all the way to the motion generation, and account for different constraints).
&
We do not agree with this comment.
The main contribution of our method are the reduction hypothesis that we are using to break the complexity of contact planning.
The problem reduction, leading to pragmatic implementation, is a step-change in how the problem of contact planning should be considered.

>>>>

In this section, we answer to each point of the reviews, while referring to the first section of the letter.

\subsection{Reviewer 1}
\noindent
\begin{longtable}{|p{21em}|p{21em}|}
\hline \bf Reviewer comment & \bf Author answer \\
\hline
The paper addresses an important problem of planning robot motion involving contacts. It extends the idea of planning acyclic contacts by decoupling the issue into (1) planning a guide path for the root of the robot, and (2) planning a discrete sequence of acyclic and static equilibrium contact configurations along the path, with an interpolation of motion between two consecutive contact postures in the sequence. The introduced planner considers both collision avoidance and maintenance of desired contacts and aims at real-time or interactive performance. 
&Thanks for the comment.
\\ \hline % ----------------------------------------------------------------------------------
For the decoupled approach to work, the planned guide path must guarantee that a sequence of stable contact configurations is associated with it to execute the path with desired contacts and yet without undesired collisions; such a guide path is called “equilibrium feasible”. The issue is how to find such a guide path efficiently. One key assumption of the paper is that for cluttered environments, “most of the times” a guide path that is “contact feasible” (referring to that at least one end-effector is in contact with the environment and there is no undesired collision between the robot and the environment) is also “equilibrium feasible”. It further assumes that if the reachable space of the robot along the guide path is in collision with the environment but the robot root configuration is not in collision, called the “reachability condition”, then the guide path is “contact feasible”. With those assumptions, the paper treated guide path planning as a geometric problem and used an RRT planner to solve the problem. 
& We agree with this summary.
\\ \hline % ----------------------------------------------------------------------------------
However, the question is whether the above key assumption (of 
“contact feasible” implies “equilibrium feasible”) is reasonable. The paper did not provide justification for the assumption, and the assumption does not seem intuitive. The paper used terms such as “most of the times” and “cluttered contact planning” without clear and quantifiable definitions. With the above assumptions, planning becomes quite straightforward, and the planning algorithm used is rather conventional. 
&
We modified the paper to more rigorously discuss these hypotheses. 
We also believe that the main justification of their validity is shown by the statistical tests we provide in the result section.\newline
See Section 6 for details. 
\\ \hline % ----------------------------------------------------------------------------------
For the next problem of planning a sequence of contact configurations given a “contact feasible” root path, the paper further decomposed the problem by planning the configuration of one limb at a time, assuming the root configuration and the other limb configurations were fixed. For each limb, N sampled configurations were considered (sampled off-line), and they were indexed by the corresponding end-effector position and stored in an octree beforehand. 
Because all that was done off-line, it is not clear how N was decided. 
&
As explained in the paper, in our previous work (Tonneau et al. 2014), we discussed in details  how to choose N. We chose to refer to the paper rather than giving details  because of the space constraints of
the paper. In our experiments,
we always set $N=10000$.

@@

\\ \hline % ----------------------------------------------------------------------------------
The main issue with the proposed planner is that assumptions (commented earlier) and decisions were made in the planner conveniently in order to simplify the problem but without much justification, and there is no guarantee of a solution. The entire approach is heuristic and somewhat ad hoc. 
&
%As detailed in Section~\ref{orig} of this cover letter, we disagree regarding the fact that our approach is purely heuristic.
%We claim that the dimensionality reduction proposed to address \mP1 is an important contribution to the field.
The main contribution of the paper are the dimensionality reduction breaking the complexity of the contact planning problem.
The main reduction comes from the reachability condition used to solve subproblem \mP1, which is not a heuristic but rather an approximate condition.
Some rigorous heuristics are introduced to solve \mP2.
We therefore disagree regarding the fact that our approach is purely heuristic.

@@

\newpage
\subsection{Reviewer 2}
\noindent
\begin{longtable}{|p{21em}|p{21em}|}
\hline \bf Reviewer comment & \bf Author answer \\
\hline
The paper presents a method for producing contact plans for the locomotion of multiped robots. It decomposes the problem into two sub-problems : the computation of a guide path is which the robot is floating close enough to the environment, and subsequently the positioning of contacts on the environment along the guide.
& Thanks for this summary, that we agree with.
\\ \hline % ----------------------------------------------------------------------------------
My major concern about this piece of work is its lack of originality. The problem seems to have been well formalized and studied in numerous previous works (Hauser et al, Escande et al, etc.). The authors experiment with minor heuristic adjustments. I do not consider them as major contributions that warrant a publication in IJRR by the standards of the journal. The authors end up with the main claim of the paper being a reduced computation time in comparison with these previous works. As admitted by the authors themselves, even this gain in computation time is not really comparable to the previous works since the outputs are different (previous works go all the way to the motion generation, and account for different constraints).
&
We do not agree with this comment.
The main contribution of our method are the reduction hypothesis that we are using to break the complexity of contact planning.
The problem reduction, leading to pragmatic implementation, is a step-change in how the problem of contact planning should be considered.
